Abstractions for Multi-Sorted Substitutions

### 2023-12-14 paper/paper.tex
Update.

  Further repetition can occur due to the choice of variable
  representation. For example, for de Bruijn indices, substitution is
  usually defined in terms of renamings to allow for structural
  induction.
  With a naive approach, this would again double the amount of
  substitution machinery, as all definitions and lemmas need to be
  made first for renamings and then again for substitutions.

@@

  Note that there is no straightforward way to construct a
  multi-sorted syntax with intrinsic typing: in a direct translation,
  the type of terms \ACode{\ACon{\_⊢\_}} would be indexed by itself, which
  most proof assistants forbid to avoid breaking logical consistency.
  We conjecture that an encoding with universe codes is possible, as
  it has been done for intrinsically typed languages with dependent
  types\cite{TODO}, but those constructions come with additional
  complexity and are less suitable to automation.

@@

  Building on the operations and axioms of a \ACode{\ACon{Kit}}, we
  derive further operations:\footnote{
    The definitions are included directly in the record module of the
    Kit, so they are implicitly parameterized over a kit.
  }
  \begin{itemize}
  \item 
    We unify the definition of renamings \ACode{S₁ \ADef{→ᵣ} S₂} and
    substitutions \ACode{S₁ \ADef{→ₛ} S₂}, which differ only in whether they
    return variables or terms:
    \LibCode\KMap
    We call a value of type \ACode{S₁ \ADef{→ₖ} S₂} a \emph{map} and
    use the meta-variable \ACode{ϕ} for it.
  \item 
    A map can be applied to a variable:
    \LibCode\KAp
  \item 
    A map can be extended by a new variable or term:
    \LibCode\KExt
  \item 
    A map can be shifted, as the \ACode{\ACon{Kit}} provides the
    necessary \ACode{\AField{wk}} operation:
    \LibCode\KWkm
  \item 
    A map can be lifted, which is the operation necessary to
    move a map under a binder of sort \ACode{s}:
    \LibCode\KLift
  \item 
    There is an identity map:
    \LibCode\KId
  \item 
    There is a singleton map, which replaces \ACode{\ACon{zero}} and decreases
    all other variables by one:
    \LibCode\KSingle
  \item 
    There is a map which is equivalent to \ACode{\AField{wk}} on terms:
    \LibCode\KWeaken
  \item
    Maps have an extensional equality:
    \LibCode\KEq
  \item
    For simplicity we postulate functional extensionality:\footnote{
      The actual implementation does \emph{not} use any postulates.
      The workaround is explained in Appendix~\ref{sec:fun-ext}.
    }
    \LibCode\KFunExt
  \item
    Lifting the identity map is a (larger) identity map:
    \LibCode\KIdLift
    % \LibCode\KIdLiftProof
  \end{itemize}

@@

  Similarly as it was the case for \ACode{\ACon{Kit}} and \ACode{\ACon{Traversal}},
  the \ACode{\ACon{ComposeTraversal}} needs to be instantiated for
  abstract \ACode{\ACon{ComposeKit}}s, which then provides the actual
  four \ACode{\ACon{ComposeKit}} instances. This allows us to break
  the dependencies between the different \ACode{\AField{⋯-fusion}} lemmas,
  similar to how \ACode{\ACon{Kit}} and \ACode{\ACon{Traversal}} allowed
  us to break the dependency between traversals with renamings and substitutions.

@@

  We then define the \ACode{\ACon{ComposeTraversal}} structure,
  which provides the \ACode{\AField{⋯-fusion}} lemma for the compositions
  described by arbitrary \ACode{\ACon{ComposeKit}}s:
  \LibCode\KComposeTraversal

  Similar as for the \ACode{\ACon{Traversal}}, we derive further
  definitions from the axiom of a \ACode{\ACon{ComposeTraversal}}:
  \begin{itemize}
  \item 
    A map \ACode{ϕ} followed by a weakening is equivalent to a
    weakening followed by \ACode{ϕ} that has been lifted over the weakened
    variable:
    \LibCode\KCommLiftWeaken
    % \LibCode\KCommLiftWeakenProof
    By applying \ACode{\AField{⋯-fusion}} to this lemma, we get the same
    statement for multiple map applications:
    \LibCode\KCommLiftWeakenTraverse
    % \LibCode\KCommLiftWeakenTraverseProof
  \item 
    A weakening followed by a singleton substitution cancel each other out:
    \LibCode\KWeakenCancelsSingle
    % \LibCode\KWeakenCancelsSingleProof
    By applying \ACode{\AField{⋯-fusion}} and \ACode{\AField{⋯-id}} to
    this lemma, we get the same statement for multiple map applications:
    \LibCode\KWeakenCancelsSingleTraverse
    % \LibCode\KWeakenCancelsSingleTraverseProof
  \item 
    A singleton substitution followed by some map \ACode{ϕ} is the same
    as \ACode{ϕ} lifted over the variable of the singleton substitution
    followed by the singleton substitution with \ACode{ϕ} applied to
    its content:
    \LibCode\KDistLiftSingle
    % \LibCode\KDistLiftSingleProof
    By applying \ACode{\AField{⋯-fusion}} to this lemma, we get the
    same statement for multiple map applications:
    \LibCode\KDistLiftSingleTraverse
    % \LibCode\KDistLiftSingleTraverseProof
  \item 
    We define \ACode{\ACon{ComposeKit}} instances for each of the four
    combinations between renamings and substitutions:
    \LibCode\KComposeKitInstances
    Interestingly, the \ACode{\ADef{Cₛ}} instance has another
    \ACode{\ADef{ComposeKit}} parameter.
    This allows us to first use \ACode{\ADef{Cᵣ}} as an argument,
    which yields the \ACode{\ADef{ComposeKit}} between substitutions
    and renamings, and then use this resulting \ACode{\ADef{ComposeKit}}
    as an argument for the case with two substitutions.
    As shown below, Agda's instance resolution is up for the task:

@@

  % \AppCode\FFusionProofRest
  \AppCode\FComposeTraversal

@@

  \section{Typing}
  \label{sec:typing}
  Equipped with a notion of types and type context, we are ready to define
  the multi-sorted typing relation for System F, incorporating both
  typing and kinding:
  \AppCode\FTyping
  The interesting cases are:
  \begin{itemize}
  \item
    the variable typing constructor, which covers both expression- and
    type-variables, analogously to the variable term constructor;
  \item
    the typing \ACode{\ACon{⊢λ}} of the lambda abstraction, which
    weakens the type of the codomain \ACode{t₂}.
    This is necessary, because multi-sorted syntax allows types
    to depend on expressions, so the typing derivation for \ACode{e}
    has to account for a variable, which is not used by the type.
  \item
    the kinding constructor \ACode{\ACon{⊢τ}} states that all types
    have kind \ACode{\ACon{★}}. This is sufficient for System F as types
    are automatically well-scoped due to intrinsic scoping.
  \end{itemize}
  To teach the framework about typing, we create a structure analogously to
  \ACode{\ACon{Syntax}}:
  \LibCode\KTyping
  The instantiation for System F is straightforward:
  \AppCode\FTypingInst

@@

  We start with \ACode{\ACon{TypingKit}}s, which abstract over
  variable and term \emph{typing}, and then define a
  \ACode{\ACon{TypingTraversal}}, which provides substitution
  preserves typing for all \ACode{\ACon{TypingKit}}s.
  \LibCode\KTypingKit
  The operations are completely analog to those of a \ACode{\ACon{Kit}}, but talk
  about typing instead of terms.
  Building on the fields of a \ACode{\ACon{TypingKit}}, we define further operations:
  \begin{itemize}
  \item
    Using the variable/term typing, we can define a renaming/substitution typing:
    \LibCode\KMapTyping
    \ACode{Γ₂ \ADef{∋*/⊢*} ϕ \ADef{∶} Γ₁} states that \ACode{ϕ} is a map that takes
    terms in \ACode{Γ₁} to terms in \ACode{Γ₂}.
  \item 
    Lifting a map preserves its typing:
    \LibCode\KLiftTyping
    % \LibCode\KLiftTypingProof
  \item 
    If a variable/term has a typing, then so does its singleton renaming/substitution:
    \LibCode\KSingleTyping
    % \LibCode\KSingleTypingProof
  \end{itemize}
  To make it easier to explicitly pass typing kits,
  we define the notation \ACode{Γ₂ \ADef{∋*/⊢*[} TK \ADef{]} ϕ \ADef{∶} Γ₁}
  to stand for \ACode{Γ₂ \ADef{∋*/⊢*} ϕ \ADef{∶} Γ₁} given some
  \ACode{\ACon{TypingKit}} \ACode{TK}.
  % \LibCode\KTypingNotation

@@

  To finish our running example, we define a standard small-step
  operational semantics for System F with full reduction and prove subject reduction:
  \AppCode\FReduction
  \vspace{0mm}
  \AppCode\FSubjectReduction
  \AppCode\FSubjectReductionProofInteresting
  We only listed the cases for $\beta$-reduction, as the other cases
  follow directly from the induction hypothesis:
  \begin{itemize}
  \item The beta-reduction rule for type-application, \ACode{\ACon{β-Λ}},
    is a direct consequence of substitution preserves typing.
  \item The beta-reduction rule for value-application is almost the same,
    but requires us to additionally show that the type is not affected by the
    expression substitution. This is a direct consequence of the weakening
    used in \ACode{\ACon{⊢λ}}.
  \end{itemize}

@@

  The formal definition of the generic class can be found in
  Appendix~\ref{sec:generic-class} and the actual implementation.

@@

  \section{Case Studies}
  \label{sec:casestudies}
  Using our full implementation of the framework, we proved subject
  reduction for the following object languages:
  \begin{itemize}
  \item
    For lambda calculus with dependent function types, the framework
    just works out of the box for both deriving and instantiating the
    \ACode{\ACon{TypingTraversal}}.
    Furthermore, the \ACode{\ACon{ComposeKit}} abstraction turned out
    to be useful to prove confluence, allowing to unify certain
    lemmas, which otherwise need to be proved for both renamings and
    substitutions.
    % e.g. that for two terms \ACode{t} and \ACode{t'}
    % with \ACode{t \ACon{↪} t'} it follows that \ACode{(t \AField{⋯} ϕ)
    % \ACon{↪} (t' \AField{⋯} ϕ)} for any map \ACode{ϕ}.
  \item
    For System F with subtyping the main challenges are how to represent
    subtyping constraints and how to deal with the fact that
    substitution preserves typing is not generally true, as type variables
    have subtyping bounds that need to be respected.
    While it would be possible to use our framework only to derive
    untyped substitution and define typing contexts and type preservation
    lemmas by hand, we found an encoding, which still allows us to use the
    the \ACode{\ACon{TypingKit}} abstraction.
    Instead of binding a type variable with a subtyping constraint
    \ACode{α <: t}, we first bind the type variable as \ACode{α : ★}, and
    then bind the constraint as \ACode{c ∶ (α <: t)}. This description is
    similar to first-class constraints, but restricted enough to be
    isomorphic to the original formalization, as constraint variables
    cannot be accesses by the user.
    With that encoding substitution preserves typing is generally true
    again, enabling the use of the framework's typing contexts and
    \ACode{\ACon{TypingKit}} machinery.
    When replacing a type variable \ACode{α <: t} with a type \ACode{t'},
    which is not a subtype of \ACode{t'}, then the resulting term is still
    well-typed, but in a context with an unsatisfiable constraint.
  \item
    Object languages with pattern matching can be encoded by adding
    the sorts of the variables bound by a pattern to the pattern sort
    \ACode{\ACon{𝕡}} itself:
    \begin{quote}
    \ACode{\ACon{𝕡} \AKw{:} \ACon{List (Sort Var)} \AKw{→} \ACon{Sort NoVar}} 
    \end{quote}
    This allows the clause of a \ACode{\ACon{match}} expression to
    read the bound variables from the pattern sort and make them
    available as free variables in its body expression.
  \end{itemize}

@@

  \section{Future Work}
  \label{sec:future}
  We want to focus our future work in the following directions:
  \begin{itemize}
  \item
    Enabling more object languages by allowing subterms with less
    restrictions on the form of \ACode{S}, allowing recursive
    occurences in container types like lists and finite functions, and
    adding support for substructural types as in
    \cite{DBLP:journals/corr/abs-2005-02247}.
  \item
    Extending the class of typing relations covered by
    the \ACode{\ACon{TypingTraversal}} abstraction and identifying
    a subclass for which it can be derived.
  \item
    Incorporating a decision procedure for equational
    substitution-lemmas based on $\sigma$-calculus as in Autosubst
    \cite{DBLP:conf/itp/SchaferTS15, DBLP:conf/cpp/StarkSK19}.
  \item
    Developing abstractions and derived lemmas beyond substition and
    type preservation, e.g. for confluence or denotational semantics
    as in \cite{DBLP:journals/pacmpl/AllaisA0MM18}.
  \end{itemize}
  \vspace{10mm}

@@

  \section{Generic Class of Object Languages}
  \label{sec:generic-class}

  \section{System F with Reflection}
  \label{sec:reflection-example}

  \section{Map Equality Without Functional Extensionality}
  \label{sec:fun-ext}

  \section{Features of the Actual Implementation}
  \label{sec:features}

>>>>

  Further repetition can occur due to the choice of variable
  representation. For example, for de Bruijn indices, substitution is
  usually defined in terms of renamings to allow for structural
  induction.
  With a naive approach, this would again double the amount of
  substitution machinery, as all definitions and lemmas need to be
  written first for renamings and then again for substitutions.

@@

  Note that there is no straightforward way to construct a
  multi-sorted syntax with intrinsic typing: in a direct translation,
  the type of terms \ACode{\ACon{\_⊢\_}} would be indexed by itself, which
  most proof assistants forbid to avoid breaking logical consistency.
  We conjecture that an encoding might be possible, as it has been
  done for intrinsically typed languages with dependent
  types\cite{DBLP:conf/popl/AltenkirchK16}, but those constructions come
  with additional complexity and are less suitable to automation.

@@

  Building on the operations and axioms of a \ACode{\ACon{Kit}}, we
  derive further operations:\footnote{
    The definitions are included directly in the record module of the
    Kit, so they are implicitly parameterized over a kit.
  }
  \begin{itemize}
  \item 
    We unify the definition of renamings \ACode{S₁ \ADef{→ᵣ} S₂} and
    substitutions \ACode{S₁ \ADef{→ₛ} S₂}, which differ only in whether they
    return variables or terms:
    \LibCode\KMap
    We call a value of type \ACode{S₁ \ADef{→ₖ} S₂} a \emph{map} and
    use the meta-variable \ACode{ϕ} for it.
  \item 
    A map can be applied to a variable:
    \LibCode\KAp
  \item 
    A map can be extended by a new variable or term:
    \LibCode\KExt
  \item 
    A map can be shifted, as the \ACode{\ACon{Kit}} provides the
    necessary \ACode{\AField{wk}} operation:
    \LibCode\KWkm
  \item 
    A map can be lifted, which is the operation necessary to
    move a map under a binder of sort \ACode{s}:
    \LibCode\KLift
  \item 
    There is an identity map:
    \LibCode\KId
  \item 
    There is a singleton map, which replaces \ACode{\ACon{zero}} and decreases
    all other variables by one:
    \LibCode\KSingle
  \item 
    There is a map which is equivalent to \ACode{\AField{wk}} on terms:
    \LibCode\KWeaken
  \item
    Maps have an extensional equality:
    \LibCode\KEq
  \item
    For simplicity we postulate functional extensionality:\footnote{
      The actual implementation does \emph{not} use any postulates.
      % The workaround is explained in Appendix~\ref{sec:fun-ext}.
    }
    \LibCode\KFunExt
  \item
    Lifting the identity map is a (larger) identity map:
    \LibCode\KIdLift
    % \LibCode\KIdLiftProof
  \end{itemize}

@@

  Similarly as it was the case for \ACode{\ACon{Kit}} and \ACode{\ACon{Traversal}},
  the lemma of the \ACode{\ACon{ComposeTraversal}} needs to be proved for
  an abstract \ACode{\ACon{ComposeKit}} and in return defines the
  four concrete \ACode{\ACon{ComposeKit}} instances for us. This allows us to break
  the dependencies between the different \ACode{\AField{⋯-fusion}} lemmas,
  similar to how \ACode{\ACon{Kit}} and \ACode{\ACon{Traversal}} allowed
  us to break the dependency between traversals with renamings and substitutions.

@@

  We then define the \ACode{\ACon{ComposeTraversal}} structure,
  which provides the \ACode{\AField{⋯-fusion}} lemma for arbitrary
  \ACode{\ACon{ComposeKit}}s:
  \LibCode\KComposeTraversal

  Similar as for the \ACode{\ACon{Traversal}}, we derive further
  definitions from the axiom of a \ACode{\ACon{ComposeTraversal}}:
  \begin{itemize}
  \item 
    A map \ACode{ϕ} followed by a weakening is equivalent to a
    weakening followed by \ACode{ϕ} that has been lifted over the weakened
    variable:
    \LibCode\KCommLiftWeaken
    % \LibCode\KCommLiftWeakenProof
    By applying \ACode{\AField{⋯-fusion}} to this lemma, we get the same
    statement for multiple map applications:
    \LibCode\KCommLiftWeakenTraverse
    % \LibCode\KCommLiftWeakenTraverseProof
  \item 
    A weakening followed by a singleton substitution cancel each other out:
    \LibCode\KWeakenCancelsSingle
    % \LibCode\KWeakenCancelsSingleProof
    By applying \ACode{\AField{⋯-fusion}} and \ACode{\AField{⋯-id}} to
    this lemma, we get the same statement for multiple map applications:
    \LibCode\KWeakenCancelsSingleTraverse
    % \LibCode\KWeakenCancelsSingleTraverseProof
  \item 
    A singleton map can be swapped with any map \ACode{ϕ}:
    \LibCode\KDistLiftSingle
    % \LibCode\KDistLiftSingleProof
    By applying \ACode{\AField{⋯-fusion}} to this lemma, we get the
    same statement for multiple map applications:
    \LibCode\KDistLiftSingleTraverse
    % \LibCode\KDistLiftSingleTraverseProof
  \item 
    We define \ACode{\ACon{ComposeKit}} instances for each of the four
    combinations between renamings and substitutions:
    \LibCode\KComposeKitInstances
    Interestingly, the \ACode{\ADef{Cₛ}} instance has another
    \ACode{\ADef{ComposeKit}} parameter.
    This allows us to first use \ACode{\ADef{Cᵣ}} as an argument,
    which yields the \ACode{\ADef{ComposeKit}} between substitutions
    and renamings, and then use this resulting \ACode{\ADef{ComposeKit}}
    as an argument for the case with two substitutions.
    As shown below, Agda's instance resolution is up for the task:

@@

  % \AppCode\FFusionProofRest
  % \AppCode\FComposeTraversal

@@

  \section{Typing}
  \label{sec:typing}
  Now that we have a notion of types and type context, we are ready to define
  the multi-sorted typing relation for System F, incorporating both
  typing and kinding:
  \AppCode\FTyping
  The interesting cases are:
  \begin{itemize}
  \item
    the variable typing constructor, which covers both expression- and
    type-variables, analogously to the variable term constructor;
  \item
    the typing \ACode{\ACon{⊢λ}} of the lambda abstraction, which
    weakens the type of the codomain \ACode{t₂}.
    This is necessary, because multi-sorted syntax allows types
    to depend on expressions, so the typing derivation for \ACode{e}
    has to account for a variable, which is not used by the type.
  \item
    the kinding constructor \ACode{\ACon{⊢τ}} states that all types
    have kind \ACode{\ACon{★}}. This is sufficient for System F as types
    are automatically well-typed due to intrinsic scoping.
  \end{itemize}
  To teach the framework about typing, we create a structure analogously to
  \ACode{\ACon{Syntax}}:
  \LibCode\KTyping
  The instantiation for System F is straightforward:
  \AppCode\FTypingInst

@@

  We start with \ACode{\ACon{TypingKit}}s, which abstract over
  variable and term \emph{typing}, and then define a
  \ACode{\ACon{TypingTraversal}}, which provides
  substitution-preserves-typing for all \ACode{\ACon{TypingKit}}s.
  \LibCode\KTypingKit
  The operations are completely analogous to those of a \ACode{\ACon{Kit}}, but talk
  about typing instead of terms.
  Building on the fields of a \ACode{\ACon{TypingKit}}, we define further operations:
  \begin{itemize}
  \item
    Using the variable/term typing, we can define a renaming/substitution typing:
    \LibCode\KMapTyping
    \ACode{Γ₂ \ADef{∋*/⊢*} ϕ \ADef{∶} Γ₁} states that \ACode{ϕ} is a map that takes
    terms in \ACode{Γ₁} to terms in \ACode{Γ₂}.
  \item 
    Lifting a map preserves its typing:
    \LibCode\KLiftTyping
    % \LibCode\KLiftTypingProof
  \item 
    If a variable/term has a typing, then so does its singleton renaming/substitution:
    \LibCode\KSingleTyping
    % \LibCode\KSingleTypingProof
  \end{itemize}
  To make it easier to explicitly pass typing kits,
  we define the notation \ACode{Γ₂ \ADef{∋*/⊢*[} TK \ADef{]} ϕ \ADef{∶} Γ₁}
  to stand for \ACode{Γ₂ \ADef{∋*/⊢*} ϕ \ADef{∶} Γ₁} given some
  \ACode{\ACon{TypingKit}} \ACode{TK}.
  % \LibCode\KTypingNotation

@@

  To finish our running example, we define a standard small-step
  operational semantics for System F with full reduction and prove subject reduction:
  \AppCode\FReduction
  \vspace{0mm}
  \AppCode\FSubjectReduction
  \AppCode\FSubjectReductionProofInteresting
  We only list the cases for $\beta$-reduction, as the other cases
  follow directly from the induction hypothesis:
  \begin{itemize}
  \item The $\beta$-reduction rule for type-application, \ACode{\ACon{β-Λ}},
    is a direct consequence of substitution-preserves-typing.
  \item The $\beta$-reduction rule for value-application is almost the same,
    but requires us to additionally show that the type is not affected by the
    expression substitution.
    % This is a direct consequence of the weakening used in \ACode{\ACon{⊢λ}}.
  \end{itemize}

@@

  The formal definition of the generic class can be found in
  the supplementary material.
  % Appendix~\ref{sec:generic-class} and the actual implementation.

@@

  \section{Case Studies}
  \label{sec:casestudies}
  Using our full implementation of the framework, we proved subject
  reduction for the following object languages:
  \begin{itemize}
  \item
    For lambda calculus with dependent function types, the framework
    just works out of the box for both deriving and instantiating the
    \ACode{\ACon{TypingTraversal}}.
    Furthermore, the \ACode{\ACon{ComposeKit}} abstraction turned out
    to be useful to prove confluence, allowing to unify certain
    lemmas, which otherwise need to be proved for both renamings and
    substitutions.
    % e.g. that for two terms \ACode{t} and \ACode{t'}
    % with \ACode{t \ACon{↪} t'} it follows that \ACode{(t \AField{⋯} ϕ)
    % \ACon{↪} (t' \AField{⋯} ϕ)} for any map \ACode{ϕ}.
  \item
    For System F with subtyping the main challenges are how to represent
    subtyping constraints and how to deal with the fact that
    substitution preserves typing is not generally true, as type variables
    have subtyping bounds that need to be respected.
    While it would be possible to use our framework only to derive
    untyped substitution and define typing contexts and type preservation
    lemmas by hand, we found an encoding, which still allows us to use the
    the \ACode{\ACon{TypingKit}} abstraction.
    Instead of binding a type variable with a subtyping constraint
    \ACode{α <: t}, we first bind the type variable as \ACode{α : ★}, and
    then bind the constraint as \ACode{c ∶ (α <: t)}. This description is
    similar to first-class constraints, but restricted enough to be
    isomorphic to the original formalization, as constraint variables
    cannot be accesses by the user.
    With that encoding substitution preserves typing is generally true
    again, enabling the use of the framework's typing contexts and
    \ACode{\ACon{TypingKit}} machinery.
    When replacing a type variable \ACode{α <: t} with a type \ACode{t'},
    which is not a subtype of \ACode{t}, then the resulting term is still
    well-typed, but in a context with an unsatisfiable constraint.
  \item
    Object languages with pattern matching can be encoded by adding
    the sorts of the variables bound by a pattern to the pattern sort
    \ACode{\ACon{𝕡}} itself:
    \begin{quote}
    \ACode{\ACon{𝕡} \AKw{:} \ACon{List (Sort Var)} \AKw{→} \ACon{Sort NoVar}} 
    \end{quote}
    This allows the clause of a \ACode{\ACon{match}} expression to
    read the bound variables from the pattern sort and make them
    available as free variables in its body expression.
  \end{itemize}

@@

  \section{Future Work}
  \label{sec:future}
  We want to focus our future work in the following directions:
  \begin{itemize}
  \item
    Enabling more object languages by allowing subterms with less
    restrictions on the form of \ACode{S}, allowing recursive
    occurences in container types like lists and finite functions, and
    adding support for substructural types as in
    \cite{DBLP:journals/corr/abs-2005-02247}.
  \item
    Extending the class of typing relations covered by
    the \ACode{\ACon{TypingTraversal}} abstraction and identifying
    a subclass for which it can be derived.
  \item
    Developing a decision procedure for equational
    substitution lemmas based on $\sigma$-calculus as in Autosubst
    \cite{DBLP:conf/itp/SchaferTS15, DBLP:conf/cpp/StarkSK19}.
  \item
    Developing abstractions and derived lemmas beyond substition and
    type preservation, e.g. for confluence or denotational semantics
    as in \cite{DBLP:journals/pacmpl/AllaisA0MM18}.
  \end{itemize}

@@

  % \section{Generic Class of Object Languages}
  % \label{sec:generic-class}

  % \section{System F with Reflection}
  % \label{sec:reflection-example}

  % \section{Map Equality Without Functional Extensionality}
  % \label{sec:fun-ext}

  % \section{Features of the Actual Implementation}
  % \label{sec:features}
